Generating Random Logic Programs Using Constraint Programming

### 2020-05-15 text/paper2/line_plots.tex
Description of the experiments

% Created by tikzDevice version 0.12.3 on 2020-05-11 12:49:51
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (346.90,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle (145.35,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71, 30.69) rectangle (145.35,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 46.03) --
	(145.35, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 69.81) --
	(145.35, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 93.59) --
	(145.35, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.66, 30.69) --
	( 49.66,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.52, 30.69) --
	( 75.52,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.39, 30.69) --
	(101.39,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.25, 30.69) --
	(127.25,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 34.14) --
	(145.35, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 57.92) --
	(145.35, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 81.70) --
	(145.35, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,105.48) --
	(145.35,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.72, 30.69) --
	( 36.72,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.59, 30.69) --
	( 62.59,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.46, 30.69) --
	( 88.46,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.32, 30.69) --
	(114.32,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.19, 30.69) --
	(140.19,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.88, 34.20) --
	( 37.03, 34.26) --
	( 37.34, 34.43) --
	( 37.76, 34.78) --
	( 37.96, 34.89) --
	( 39.21, 35.94) --
	( 44.56, 37.96) --
	( 44.72, 37.05) --
	( 45.03, 37.14) --
	( 47.07, 39.24) --
	( 52.24, 42.35) --
	( 52.40, 40.98) --
	( 52.71, 41.86) --
	( 60.08, 44.75) --
	( 60.39, 44.97) --
	( 67.76, 48.70) --
	( 67.92, 47.86) --
	( 68.07, 47.05) --
	( 68.23, 47.32) --
	( 68.85, 49.64) --
	( 75.75, 52.22) --
	( 83.44, 55.11) --
	( 91.12, 58.33) --
	( 98.80, 75.16) --
	( 99.11, 59.59) --
	( 99.73, 62.82) --
	(130.00, 75.17) --
	(130.62, 78.87) --
	(140.19, 88.26);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 36.88, 34.22) --
	( 37.03, 34.33) --
	( 37.34, 37.18) --
	( 37.76, 37.64) --
	( 37.96, 43.41) --
	( 39.21, 42.20) --
	( 44.56, 57.46) --
	( 44.72, 36.84) --
	( 45.03, 37.68) --
	( 47.07, 40.19) --
	( 52.24, 42.81) --
	( 52.40, 41.77) --
	( 52.71, 40.98) --
	( 60.08, 45.16) --
	( 60.39, 49.30) --
	( 67.76, 47.31) --
	( 67.92, 55.25) --
	( 68.07, 48.59) --
	( 68.23, 46.96) --
	( 68.85, 47.72) --
	( 75.75, 52.99) --
	( 83.44, 57.55) --
	( 91.12, 56.42) --
	( 98.80, 71.23) --
	( 99.11, 62.93) --
	( 99.73, 67.49) --
	(130.00, 79.80) --
	(130.62, 85.06) --
	(140.19, 91.20);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 36.88, 34.22) --
	( 37.03, 34.29) --
	( 37.34, 34.49) --
	( 37.76, 34.88) --
	( 37.96, 35.00) --
	( 39.21, 36.19) --
	( 44.56, 38.30) --
	( 44.72, 37.18) --
	( 45.03, 37.98) --
	( 47.07, 40.27) --
	( 52.24, 44.88) --
	( 52.40, 42.06) --
	( 52.71, 40.35) --
	( 60.08, 45.65) --
	( 60.39, 47.17) --
	( 67.76, 51.25) --
	( 67.92, 52.15) --
	( 68.07, 51.25) --
	( 68.23, 52.79) --
	( 68.85, 51.87) --
	( 75.75, 54.08) --
	( 83.44, 57.97) --
	( 91.12, 61.03) --
	( 98.80, 76.47) --
	( 99.11, 65.20) --
	( 99.73, 59.83) --
	(130.00, 84.23) --
	(130.62, 85.33) --
	(140.19, 99.28);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 36.88, 34.24) --
	( 37.03, 34.31) --
	( 37.34, 34.50) --
	( 37.76, 34.90) --
	( 37.96, 35.05) --
	( 39.21, 36.07) --
	( 44.56, 38.21) --
	( 44.72, 38.54) --
	( 45.03, 38.69) --
	( 47.07, 40.00) --
	( 52.24, 42.70) --
	( 52.40, 41.93) --
	( 52.71, 41.20) --
	( 60.08, 46.14) --
	( 60.39, 46.70) --
	( 67.76, 50.70) --
	( 67.92, 48.30) --
	( 68.07, 50.28) --
	( 68.23, 47.98) --
	( 68.85, 52.07) --
	( 75.75, 55.24) --
	( 83.44, 59.51) --
	( 91.12, 61.81) --
	( 98.80, 82.15) --
	( 99.11, 68.77) --
	( 99.73, 67.98) --
	(130.00, 80.96) --
	(130.62, 80.15) --
	(140.19, 97.28);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 36.88, 34.20) --
	( 37.03, 34.32) --
	( 37.34, 34.48) --
	( 37.76, 34.84) --
	( 37.96, 34.97) --
	( 39.21, 35.75) --
	( 44.56, 37.97) --
	( 44.72, 36.07) --
	( 45.03, 38.73) --
	( 47.07, 40.22) --
	( 52.24, 44.23) --
	( 52.40, 43.29) --
	( 52.71, 40.97) --
	( 60.08, 46.70) --
	( 60.39, 47.27) --
	( 67.76, 50.76) --
	( 67.92, 53.24) --
	( 68.07, 51.86) --
	( 68.23, 53.84) --
	( 68.85, 51.03) --
	( 75.75, 54.08) --
	( 83.44, 59.44) --
	( 91.12, 63.01) --
	( 98.80, 79.72) --
	( 99.11, 66.18) --
	( 99.73, 66.97) --
	(130.00, 83.43) --
	(130.62, 87.45) --
	(140.19, 98.97);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 36.88, 34.23) --
	( 37.03, 34.28) --
	( 37.34, 34.44) --
	( 37.76, 34.80) --
	( 37.96, 34.97) --
	( 39.21, 36.01) --
	( 44.56, 37.80) --
	( 44.72, 36.11) --
	( 45.03, 37.78) --
	( 47.07, 39.38) --
	( 52.24, 43.57) --
	( 52.40, 41.73) --
	( 52.71, 43.60) --
	( 60.08, 45.48) --
	( 60.39, 45.53) --
	( 67.76, 46.06) --
	( 67.92, 48.49) --
	( 68.07, 47.82) --
	( 68.23, 50.65) --
	( 68.85, 47.58) --
	( 75.75, 51.59) --
	( 83.44, 56.58) --
	( 91.12, 55.51) --
	( 98.80, 75.37) --
	( 99.11, 65.39) --
	( 99.73, 59.41) --
	(130.00, 80.88) --
	(130.62, 80.85) --
	(140.19, 91.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (145.35,108.01);
\end{scope}
\begin{scope}
\path[clip] (150.85, 30.69) rectangle (264.49,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (150.85, 30.69) rectangle (264.49,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 46.03) --
	(264.49, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 69.81) --
	(264.49, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 93.59) --
	(264.49, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (168.93, 30.69) --
	(168.93,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (194.76, 30.69) --
	(194.76,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (220.59, 30.69) --
	(220.59,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (246.42, 30.69) --
	(246.42,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 34.14) --
	(264.49, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 57.92) --
	(264.49, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 81.70) --
	(264.49, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85,105.48) --
	(264.49,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 30.69) --
	(156.02,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (181.85, 30.69) --
	(181.85,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.67, 30.69) --
	(207.67,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.50, 30.69) --
	(233.50,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.33, 30.69) --
	(259.33,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 82.69) --
	(159.71, 86.86) --
	(167.09, 90.51) --
	(170.78, 84.86) --
	(173.24, 90.95) --
	(185.54, 87.17) --
	(189.23, 82.10) --
	(200.29, 86.31) --
	(211.36, 91.58) --
	(215.05, 82.04) --
	(218.74, 87.00) --
	(224.89, 82.36) --
	(226.12, 81.20) --
	(229.81, 82.46) --
	(233.50, 88.61) --
	(237.19, 93.14) --
	(240.88, 91.31) --
	(251.95, 83.85) --
	(255.64, 86.37) --
	(259.33, 89.25);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (156.02, 91.65) --
	(159.71, 90.13) --
	(167.09, 92.54) --
	(170.78, 85.10) --
	(173.24, 93.89) --
	(185.54, 91.81) --
	(189.23, 87.37) --
	(200.29, 88.45) --
	(211.36, 94.07) --
	(215.05, 85.46) --
	(218.74, 89.07) --
	(224.89, 81.32) --
	(226.12, 84.81) --
	(229.81, 85.30) --
	(233.50, 90.02) --
	(237.19, 93.14) --
	(240.88, 94.41) --
	(251.95, 85.94) --
	(255.64, 89.62) --
	(259.33, 93.56);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (156.02, 96.40) --
	(159.71, 96.07) --
	(167.09,104.50) --
	(170.78, 94.79) --
	(173.24,102.91) --
	(185.54,101.57) --
	(189.23, 94.35) --
	(200.29, 98.68) --
	(211.36,103.55) --
	(215.05, 88.61) --
	(218.74, 97.59) --
	(224.89, 89.92) --
	(226.12, 91.22) --
	(229.81, 87.06) --
	(233.50, 98.75) --
	(237.19,102.58) --
	(240.88,102.50) --
	(251.95, 90.37) --
	(255.64, 96.15) --
	(259.33,100.82);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (156.02, 90.92) --
	(159.71,100.08) --
	(167.09, 97.34) --
	(170.78, 90.63) --
	(173.24, 99.99) --
	(185.54, 96.84) --
	(189.23, 91.32) --
	(200.29, 97.00) --
	(211.36,100.90) --
	(215.05, 88.00) --
	(218.74, 94.45) --
	(224.89, 92.66) --
	(226.12, 90.99) --
	(229.81, 92.19) --
	(233.50, 96.98) --
	(237.19, 99.26) --
	(240.88,100.29) --
	(251.95, 92.01) --
	(255.64, 93.41) --
	(259.33, 99.52);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (156.02, 91.47) --
	(159.71, 96.45) --
	(167.09,104.39) --
	(170.78, 90.59) --
	(173.24,102.58) --
	(185.54,100.46) --
	(189.23, 95.50) --
	(200.29, 97.48) --
	(211.36,103.31) --
	(215.05, 90.65) --
	(218.74, 97.90) --
	(224.89, 87.48) --
	(226.12, 91.85) --
	(229.81, 91.08) --
	(233.50, 98.02) --
	(237.19,100.29) --
	(240.88,102.81) --
	(251.95, 90.81) --
	(255.64, 95.58) --
	(259.33,101.07);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (156.02, 81.98) --
	(159.71, 88.47) --
	(167.09, 93.40) --
	(170.78, 85.56) --
	(173.24, 94.47) --
	(185.54, 91.91) --
	(189.23, 83.83) --
	(200.29, 92.87) --
	(211.36, 94.86) --
	(215.05, 82.23) --
	(218.74, 90.48) --
	(224.89, 86.23) --
	(226.12, 82.27) --
	(229.81, 80.81) --
	(233.50, 91.75) --
	(237.19, 92.55) --
	(240.88, 93.28) --
	(251.95, 85.59) --
	(255.64, 87.94) --
	(259.33, 93.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (150.85, 30.69) rectangle (264.49,108.01);
\end{scope}
\begin{scope}
\path[clip] ( 31.71,108.01) rectangle (145.35,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,108.01) rectangle (145.35,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.53,113.27) {The number of facts ($\times 10^3$)};
\end{scope}
\begin{scope}
\path[clip] (150.85,108.01) rectangle (264.49,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (150.85,108.01) rectangle (264.49,124.59);
\definecolor{drawColor}{gray}{0.10}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-15 17:19:15
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (346.90,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle (146.09,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71, 30.69) rectangle (146.09,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 46.03) --
	(146.09, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 69.81) --
	(146.09, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 93.59) --
	(146.09, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.77, 30.69) --
	( 49.77,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.80, 30.69) --
	( 75.80,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.84, 30.69) --
	(101.84,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.87, 30.69) --
	(127.87,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 34.14) --
	(146.09, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 57.92) --
	(146.09, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 81.70) --
	(146.09, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,105.48) --
	(146.09,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.75, 30.69) --
	( 36.75,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.79, 30.69) --
	( 62.79,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.82, 30.69) --
	( 88.82,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.85, 30.69) --
	(114.85,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.89, 30.69) --
	(140.89,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.91, 34.22) --
	( 37.07, 34.28) --
	( 37.38, 34.45) --
	( 37.80, 34.74) --
	( 38.00, 34.74) --
	( 39.25, 35.27) --
	( 44.64, 37.45) --
	( 44.80, 36.38) --
	( 45.11, 37.84) --
	( 47.17, 39.46) --
	( 52.37, 41.24) --
	( 52.53, 41.31) --
	( 52.84, 41.51) --
	( 60.26, 45.33) --
	( 60.58, 45.62) --
	( 67.99, 50.08) --
	( 68.15, 47.64) --
	( 68.31, 50.15) --
	( 68.46, 46.59) --
	( 69.09, 54.70) --
	( 76.04, 53.02) --
	( 83.77, 56.41) --
	( 91.50, 57.95) --
	( 99.23, 74.63) --
	( 99.55, 65.78) --
	(100.17, 64.84) --
	(130.63, 79.54) --
	(131.26, 78.48) --
	(140.89, 91.54);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 36.91, 34.20) --
	( 37.07, 34.26) --
	( 37.38, 34.41) --
	( 37.80, 34.70) --
	( 38.00, 34.68) --
	( 39.25, 35.23) --
	( 44.64, 37.74) --
	( 44.80, 37.05) --
	( 45.11, 37.14) --
	( 47.17, 39.19) --
	( 52.37, 42.35) --
	( 52.53, 40.98) --
	( 52.84, 41.86) --
	( 60.26, 44.75) --
	( 60.58, 45.01) --
	( 67.99, 48.70) --
	( 68.15, 46.51) --
	( 68.31, 47.05) --
	( 68.46, 47.32) --
	( 69.09, 49.64) --
	( 76.04, 52.22) --
	( 83.77, 55.11) --
	( 91.50, 58.33) --
	( 99.23, 75.16) --
	( 99.55, 59.59) --
	(100.17, 62.82) --
	(130.63, 75.24) --
	(131.26, 79.11) --
	(140.89, 88.23);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 36.91, 34.22) --
	( 37.07, 34.33) --
	( 37.38, 34.49) --
	( 37.80, 34.77) --
	( 38.00, 34.77) --
	( 39.25, 35.37) --
	( 44.64, 37.40) --
	( 44.80, 36.84) --
	( 45.11, 37.68) --
	( 47.17, 39.58) --
	( 52.37, 42.81) --
	( 52.53, 41.77) --
	( 52.84, 40.98) --
	( 60.26, 45.16) --
	( 60.58, 45.74) --
	( 67.99, 47.31) --
	( 68.15, 46.52) --
	( 68.31, 48.59) --
	( 68.46, 46.96) --
	( 69.09, 47.72) --
	( 76.04, 52.99) --
	( 83.77, 57.55) --
	( 91.50, 56.42) --
	( 99.23, 71.23) --
	( 99.55, 62.93) --
	(100.17, 67.49) --
	(130.63, 75.36) --
	(131.26, 79.09) --
	(140.89, 90.92);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 36.91, 34.22) --
	( 37.07, 34.29) --
	( 37.38, 34.48) --
	( 37.80, 34.79) --
	( 38.00, 34.74) --
	( 39.25, 35.45) --
	( 44.64, 37.64) --
	( 44.80, 37.18) --
	( 45.11, 37.98) --
	( 47.17, 40.20) --
	( 52.37, 44.88) --
	( 52.53, 42.06) --
	( 52.84, 40.35) --
	( 60.26, 45.65) --
	( 60.58, 47.25) --
	( 67.99, 51.25) --
	( 68.15, 51.16) --
	( 68.31, 51.25) --
	( 68.46, 52.79) --
	( 69.09, 51.87) --
	( 76.04, 54.08) --
	( 83.77, 57.97) --
	( 91.50, 61.03) --
	( 99.23, 76.47) --
	( 99.55, 65.20) --
	(100.17, 59.83) --
	(130.63, 84.66) --
	(131.26, 85.31) --
	(140.89, 99.29);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 36.91, 34.24) --
	( 37.07, 34.31) --
	( 37.38, 34.48) --
	( 37.80, 34.81) --
	( 38.00, 34.77) --
	( 39.25, 35.45) --
	( 44.64, 37.88) --
	( 44.80, 38.54) --
	( 45.11, 38.69) --
	( 47.17, 39.95) --
	( 52.37, 42.70) --
	( 52.53, 41.93) --
	( 52.84, 41.20) --
	( 60.26, 46.14) --
	( 60.58, 46.43) --
	( 67.99, 50.70) --
	( 68.15, 47.87) --
	( 68.31, 50.28) --
	( 68.46, 47.98) --
	( 69.09, 52.07) --
	( 76.04, 55.24) --
	( 83.77, 59.51) --
	( 91.50, 61.81) --
	( 99.23, 82.15) --
	( 99.55, 68.77) --
	(100.17, 67.98) --
	(130.63, 80.43) --
	(131.26, 80.51) --
	(140.89, 97.30);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 36.91, 34.20) --
	( 37.07, 34.32) --
	( 37.38, 34.47) --
	( 37.80, 34.80) --
	( 38.00, 34.78) --
	( 39.25, 35.44) --
	( 44.64, 37.83) --
	( 44.80, 36.07) --
	( 45.11, 38.73) --
	( 47.17, 40.20) --
	( 52.37, 44.23) --
	( 52.53, 43.29) --
	( 52.84, 40.97) --
	( 60.26, 46.70) --
	( 60.58, 47.28) --
	( 67.99, 50.76) --
	( 68.15, 52.81) --
	( 68.31, 51.86) --
	( 68.46, 53.84) --
	( 69.09, 51.03) --
	( 76.04, 54.08) --
	( 83.77, 59.44) --
	( 91.50, 63.01) --
	( 99.23, 79.72) --
	( 99.55, 66.18) --
	(100.17, 66.97) --
	(130.63, 83.22) --
	(131.26, 87.08) --
	(140.89, 98.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (146.09,108.01);
\end{scope}
\begin{scope}
\path[clip] (151.59, 30.69) rectangle (265.96,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (151.59, 30.69) rectangle (265.96,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (151.59, 46.03) --
	(265.96, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (151.59, 69.81) --
	(265.96, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] (151.59, 93.59) --
	(265.96, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.78, 30.69) --
	(169.78,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.78, 30.69) --
	(195.78,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (221.77, 30.69) --
	(221.77,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (247.77, 30.69) --
	(247.77,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59, 34.14) --
	(265.96, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59, 57.92) --
	(265.96, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59, 81.70) --
	(265.96, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59,105.48) --
	(265.96,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.79, 30.69) --
	(156.79,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (182.78, 30.69) --
	(182.78,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (208.77, 30.69) --
	(208.77,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (234.77, 30.69) --
	(234.77,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (260.76, 30.69) --
	(260.76,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.79, 87.17) --
	(160.50, 93.17) --
	(167.93, 93.97) --
	(171.64, 85.86) --
	(174.11, 95.63) --
	(186.49, 90.99) --
	(190.21, 86.16) --
	(201.35, 88.72) --
	(212.49, 93.71) --
	(216.20, 85.21) --
	(219.91, 88.26) --
	(226.10, 81.94) --
	(227.34, 84.46) --
	(231.05, 82.43) --
	(234.77, 92.42) --
	(238.48, 95.04) --
	(242.19, 93.76) --
	(253.34, 84.82) --
	(257.05, 89.64) --
	(260.76, 94.51);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (156.79, 81.98) --
	(160.50, 87.03) --
	(167.93, 90.51) --
	(171.64, 84.86) --
	(174.11, 90.95) --
	(186.49, 87.07) --
	(190.21, 82.10) --
	(201.35, 86.31) --
	(212.49, 91.58) --
	(216.20, 81.17) --
	(219.91, 86.92) --
	(226.10, 82.36) --
	(227.34, 81.20) --
	(231.05, 82.46) --
	(234.77, 88.61) --
	(238.48, 93.14) --
	(242.19, 91.31) --
	(253.34, 83.85) --
	(257.05, 86.37) --
	(260.76, 89.25);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (156.79, 88.97) --
	(160.50, 89.35) --
	(167.93, 92.54) --
	(171.64, 85.10) --
	(174.11, 93.89) --
	(186.49, 90.38) --
	(190.21, 87.37) --
	(201.35, 88.45) --
	(212.49, 94.07) --
	(216.20, 82.90) --
	(219.91, 88.35) --
	(226.10, 81.32) --
	(227.34, 84.81) --
	(231.05, 85.30) --
	(234.77, 90.02) --
	(238.48, 93.14) --
	(242.19, 94.41) --
	(253.34, 85.94) --
	(257.05, 89.62) --
	(260.76, 93.56);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (156.79, 95.74) --
	(160.50, 96.35) --
	(167.93,104.50) --
	(171.64, 94.79) --
	(174.11,102.91) --
	(186.49,101.65) --
	(190.21, 94.35) --
	(201.35, 98.68) --
	(212.49,103.55) --
	(216.20, 88.20) --
	(219.91, 97.47) --
	(226.10, 89.92) --
	(227.34, 91.22) --
	(231.05, 87.06) --
	(234.77, 98.75) --
	(238.48,102.58) --
	(242.19,102.50) --
	(253.34, 90.37) --
	(257.05, 96.15) --
	(260.76,100.82);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (156.79, 90.34) --
	(160.50,100.33) --
	(167.93, 97.34) --
	(171.64, 90.63) --
	(174.11, 99.99) --
	(186.49, 96.75) --
	(190.21, 91.32) --
	(201.35, 97.00) --
	(212.49,100.90) --
	(216.20, 88.11) --
	(219.91, 94.51) --
	(226.10, 92.66) --
	(227.34, 90.99) --
	(231.05, 92.19) --
	(234.77, 96.98) --
	(238.48, 99.26) --
	(242.19,100.29) --
	(253.34, 92.01) --
	(257.05, 93.41) --
	(260.76, 99.52);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (156.79, 90.96) --
	(160.50, 96.67) --
	(167.93,104.39) --
	(171.64, 90.59) --
	(174.11,102.58) --
	(186.49,100.48) --
	(190.21, 95.50) --
	(201.35, 97.48) --
	(212.49,103.31) --
	(216.20, 90.87) --
	(219.91, 97.96) --
	(226.10, 87.48) --
	(227.34, 91.85) --
	(231.05, 91.08) --
	(234.77, 98.02) --
	(238.48,100.29) --
	(242.19,102.81) --
	(253.34, 90.81) --
	(257.05, 95.58) --
	(260.76,101.07);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.59, 30.69) rectangle (265.96,108.01);
\end{scope}
\begin{scope}
\path[clip] ( 31.71,108.01) rectangle (146.09,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,108.01) rectangle (146.09,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.90,113.27) {The number of facts ($\times 10^3$)};
\end{scope}
\begin{scope}
\path[clip] (151.59,108.01) rectangle (265.96,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (151.59,108.01) rectangle (265.96,124.59);
\definecolor{drawColor}{gray}{0.10}
